\documentclass[margin,line]{res}
% Define colors for use in hyper-links
\usepackage{color}
    \definecolor{link-gray}{gray}{0}
    \definecolor{box-gray}{gray}{1}
\usepackage[colorlinks=true, linkcolor=link-gray, citecolor=link-gray, filecolor=link-gray, menucolor=link-gray, urlcolor=link-gray]{hyperref}
% Font packages
%\usepackage{mathpazo}
%\usepackage{helvet}
%\usepackage{mathptmx}

\def\UrlFont{}

\hypersetup{
  pdfauthor = {Michael Carbajales-Dale},
  pdftitle = {Biographical sketch},
  pdfsubject = {},
  pdfkeywords = {},
  pdfcreator = {LaTeX with hyperref package}
}

%\usepackage{mathptmx}



\oddsidemargin 0in
\evensidemargin -.5in
\textwidth=5.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0.04in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0.04in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{} \chead{} \rhead{}
\lfoot{\small{M. Carbajales-Dale}} \cfoot{\small{Biographical sketch}} \rfoot{\small{\thepage}}
\fancypagestyle{plain}{\fancyfoot[RO,RE]{\thepage}}
\renewcommand\headrulewidth{0pt}
\renewcommand\footrulewidth{0.1pt}



\begin{document}

\name{Michael Carbajales-Dale \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{lrl}
Clemson University										& {\it email:}   	& madale@clemson.edu 	\\
Rich Lab, Rm 160											& {\it voice:}   	& (864) 656-0523			\\
Computer Court                            				& {\it fax:}     	& (864) 656-0672			\\
Anderson, SC 29625                      				&{\it skype:}		& mikdale							\\

\end{tabular}

\section{\sc Professional \\ Preparation}
\begin{itemize}
\setlength{\itemsep}{0pt}
	\item	University of Bristol, UK, \emph{Physics \& Philosophy} \hfill {\textbf{MSci}, 2006}
	\item	University of Canterbury, NZ, \emph{Mechanical Engineering} \hfill {\textbf{PhD}, 2011}
	\item	Stanford University, CA \emph{Energy Systems Analysis}	\hfill{\textbf{Post-doc}, 2011-2013} 			
\end{itemize}

\section{\sc Appointments}
\begin{itemize}
\setlength{\itemsep}{0pt}
	\item	\textbf{Assistant Professor} \hfill {Aug 2014 to Present}\\
				Environmental Engineering \& Earth Sciences, \emph{Clemson University}, SC 
	\item	\textbf{Research Associate} \hfill {Feb 2014 to Jul 2014}\\
				Environmental Assessment \& Optimization Group, \emph{Stanford University}, CA 
	\item	\textbf{Teaching Fellow} \hfill {Aug 2013 to Jan 2014}\\
				Thinking Matters: Energy, \emph{Stanford University}, CA 
	\item	\textbf{Post-doctoral Researcher} \hfill {Feb 2011 to Aug 2013}\\
				Global Climate and Energy Project, \emph{Stanford University}, CA
\end{itemize}

\section{\sc Related \\ Publications}
\begin{itemize}
\setlength{\itemsep}{0pt}
	\item	Heun, M; \textbf{Carbajales-Dale, M.}; Haney, B. (2013) 
				Beyond GDP: National Accounting in the Age of Resource Depletion
				\emph{Springer}
	
	\item 	\textbf{Carbajales-Dale, M.}; Barnhart, C. J.; and Benson, S. M. (2014)
				Can we afford storage?
				A dynamic net energy analysis of renewable electricity generation 
				firmed by energy storage,
				\emph{Energy \& Environmental Science}, DOI:10.1039/C3EE42125B.
				
	\item 	Barnhart, C. J.; \textbf{Dale, M.}; Brandt, A. R. and Benson, S. M. (2013)
				The energetic implications of curtailing versus storing solar-
				and wind-generated electricity,
				\emph{Energy \& Environmental Science}, 6, 2804-2810	
							
	\item	\textbf{Dale, M.} (2013) 
				A comparative analysis of energy consumption by 
				renewable energy technologies, 
				\emph{Applied Sciences}, 3, 325-337	
				
	\item 	\textbf{Dale, M.} and Benson, S. M. (2013) 
				The Energy Balance of the Photovoltaic (PV) Industry --- 
				Is the PV Industry a Net Energy Provider? 
				\emph{Environmental Science \& Technology}, 47(7), 3482-3489
			
\end{itemize}

\section{\sc Other \\ Publications}
\begin{itemize}
\setlength{\itemsep}{0pt}
	\item	Brandt, A. R.; \textbf{Dale, M.} and Barnhart, C. J. (2013)
				Calculating systems-scale energy efficiency and net energy returns: 
				A bottom-up matrix-based approach
				\emph{Energy}, 62, 235-247	

%	\item	Murphy, D. J.; Hall, C. A. S.; \textbf{Dale, M.} and Cleveland, C. (2011) 
%				Order from Chaos: 
%				A Preliminary Protocol for Determining the EROI of Fuels, 
%				\emph{Sustainability}, 3 (10), 1888-1907
%				
	\item	Brandt, A. R.; and \textbf{Dale, M.} (2011)
				A general mathematical framework for calculating 
				systems-scale efficiency of energy extraction and conversion: 
				Energy return on investment (EROI) and other energy return ratios
				\emph{Energies}, 4, 1211-1245	
				
	\item	\textbf{Dale, M.}; Krumdieck, S. and Bodger, P. (2011) 
				A Dynamic Function for EROI, 
				\emph{Sustainability}, 3 (10), 1972-1985

	\item	\textbf{Dale, M.}; Krumdieck, S. and Bodger, P. (2011) 
				Global energy modelling---A biophysical approach (GEMBA) Part 2: Methodology,
				\emph{Ecological Economics}, 73, 158-167
%
%	\item	\textbf{Dale, M.}; Krumdieck, S. and Bodger, P. (2011) 
%				Net energy yield from production of conventional oil
%				\emph{Energy Policy}, 39 (11), 7095-7102
\end{itemize}

\section{\sc Synergistic \\ Activities}
\begin{itemize}
\setlength{\itemsep}{0pt}
	\item	Developed the \emph{Global Energy Modeling - a Biophysical Approach} (GEMBA)
				methodology and model, which is currently being used by researchers world-wide to
				explore the impact of resource depletion on future energy scenarios.
				
	\item	Undertook meta-analysis of energetic costs of photovoltaic (PV), 
				concentrating solar power and wind electricity generating technologies.
	
	\item	Developed model to track changes in cumulative energy demand for 
				manufacture of PV systems.
				
	\item	Developed curricula for several classes including:
				\begin{itemize}
				\setlength{\itemsep}{0pt}
					\begin{small}
					\item	EES 8200:	\emph{Environmental Systems Analysis}, Clemson University

					\item	EES 4860/6860: \emph{Environmental Sustainability}, Clemson University
					
					\item	Freshman: \emph{Energy? Understanding the challenge, developing solutions}, Stanford University
					
					\item	Energy 101: \emph{Energy and the environment}, Stanford University
					\end{small}
				\end{itemize}
\end{itemize}

\section{\sc Collaborators \\ and Co-Editors}
\begin{itemize}
\setlength{\itemsep}{0pt}
	\item	Mr. Jim Baldauf	,	\emph{Association for the Study of Peak Oil}
	\item	Prof. Charles Barnhart, \emph{Western Washington University}
	\item	Prof. Pat Bodger, \emph{University of Canterbury}, New Zealand
	\item	Prof. Adam Brandt, \emph{Stanford University}
	\item	Prof. Cutler Cleveland, \emph{Boston University}
	\item	Prof. Chris Field, \emph{Stanford University}
	\item	Dr. Nathan Hagens,	\emph{Institute for Integrated Economic Research}
	\item	Prof. Charles Hall, \emph{SUNY, Syracuse} emeritus
	\item	Prof. Becky Haney,	\emph{Calvin College}, Michigan
	\item	Prof. Matthew Heun,	 \emph{Calvin College}, Michigan
	\item	Prof. Michael Jefferson, \emph{University of Buckingham}, United Kingdom
	\item	Mr. Rembrandt Koppelaar,	\emph{Imperial University}, United Kingdom
	\item	Dr. Carey King,		\emph{University of Texas at Austin}
	\item	Prof. Susan Krumdieck, \emph{University of Canterbury}, New Zealand
	\item	Dr. Hannes Kunz,	\emph{Institute for Integrated Economic Research}
	\item 	Mr. Jean Laherrere,	\emph{Oil Depletion Analysis Centre}
	\item	Prof. David Lobell, \emph{Stanford University}
	\item 	Dr. Kerry Mulligan, \emph{University of Canterbury}, New Zealand
	\item	Dr. David Murphy, \emph{Northern Illinois University}
	\item	Mr. Chris Nelder,	\emph{SmartPlanet}
	\item	Dr. Shannon Page, \emph{Lincoln University}, New Zealand
	\item	Prof. Sujith Ravi,	\emph{Temple University}
	\item	Dr. Stacy Rendall, \emph{University of Canterbury}, New Zealand
\end{itemize}

\section{\sc Graduate \\ Advisers \& \\ Postdoctoral \\ Sponsors}
\begin{itemize}
\setlength{\itemsep}{0pt}
	\item	Prof. Pat Bodger, \emph{University of Canterbury}, New Zealand
	\item	Prof. Susan Krumdieck, \emph{University of Canterbury}, New Zealand
	\item	Dr. Keith Morrison, \emph{Lincoln University}, New Zealand
	\item	Prof. John Peet,	\emph{University of Canterbury} emeritus, New Zealand
	\item	Prof. Sally Benson, \emph{Global Climate and Energy Project}, Stanford University
\end{itemize}

\section{\sc Graduate Students}
\begin{itemize}
\setlength{\itemsep}{0pt}
	\item Total: 6 graduate students (3 Masters, 3 PhD)
\end{itemize}
\end{resume}
\end{document}
